Summary of the First Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE1)

### 2014-04-24 WSSSPE1_report/WSSSPE1_summary_report.tex
fixing author bug

\author{Daniel~S.~Katz$^{(1)}$,
Sou-Cheng~T.~Choi$^{(2)}$,
Hilmar~Lapp$^{(3)}$,
Ketan~Maheshwari$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Matthew~Turk$^{(6)}$,
Marcus~D.~Hanwell$^{(7)}$,
Nancy~Wilkins-Diehr$^{(8)}$,
James~Hetherington$^{(9)}$,
James~Howison$^{(10)}$,
Shel~Swenson$^{(11)}$,
Gabrielle~D.~Allen$^{(12)}$,
Bruce~Berriman$^{(11)}$
Colin~Venters$^{(14)}$
}

>>>>

\author{Daniel~S.~Katz$^{(1)}$,
Sou-Cheng~T.~Choi$^{(2)}$,
Hilmar~Lapp$^{(3)}$,
Ketan~Maheshwari$^{(4)}$,
Frank~L\"{o}ffler$^{(5)}$,
Matthew~Turk$^{(6)}$,
Marcus~D.~Hanwell$^{(7)}$,
Nancy~Wilkins-Diehr$^{(8)}$,
James~Hetherington$^{(9)}$,
James~Howison$^{(10)}$,
Shel~Swenson$^{(11)}$,
Gabrielle~D.~Allen$^{(12)}$,
Bruce~Berriman$^{(13)}$
Colin~Venters$^{(14)}$
}
